Grocery stores in Canada

### 2024-11-14 paper/paper.qmd
removed unused packages in paper.qmd

```{r}
#| include: false
#| warning: false
#| message: false
#install.packages('opendatatoronto')
#install.packages("dplyr")
#install.packages('tidyverse')
#install.packages('sf')
#remove.packages('knitr')S
#install.packages('knitr')
#install.packages('ggplot2)

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
#install.packages('ggplot2)
